 Casting multiple shadows: interactive data visualisation with tours and embeddings

### 2020-02-07 paper.Rmd
add posing queries

>>>>

We combine the tour view in a side by side layout with a scatter
plot view from an embedding algorithm. The views are linked; analysts can brush a group of points in the embedding view, and see its shape in the tour view.
This can be used for either manually identifying clusers, or verifying the location of clusters relative to other groupings. Consequently, simple linked
brushing can alleviate a downfall of non-linear methods such as UMAP or t-SNE
that break hierachial structure of clusterings. Aside from simple
linked brushing, we can also pose more complex queries via interrogating
the neighbourhood graph. Using a linked neighbourhood brush, we can 
visually investigate the nearest neighbour relationships in the 
high-dimensional space via brushing in the embedding view. The user can select
the number of nearest neighbours directly, and modify the distance metric 
used for determining the neighbours. This allows users to interrogate the stability of clusters generated in the embedding view. Multiple brushes
can be used to pose queries in either the tour view or the embedding view;
interface controls allow these brushes to combine using logical operators
such as 'and', 'or', or 'not'. The use of linked brushing goes beyond
single point highlights or colorings, allowing analysts to get a more holistic
view of the effect of an embedding algorithm.
